---
title: "Análises"
output: html_notebook
---

```{r setup, include=FALSE}


library(flextable)
library(tidyverse)
library(readxl)
library(olsrr)
library(lmtest)
library(corrplot)
library(gridExtra)
library(stargazer)

sistemas_total <- read.csv("../dados/sistemas_constitucionais_ccp_v4.csv")

ccp_tratada <- read.csv("../dados/ccp_tratada_valida.csv")

```

## Variáveis dependentes

### Bicameralismo:

Frequência simples:


```{r echo=FALSE}

ccp_tratada |> 
  count(bicameralismo) |> 
  mutate(Percentual = round(n/sum(n)*100,1))



```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
